\documentclass{article}

\title{Lab 6 Report}
\author{Karthik}
\date{\today}

\begin{document}

\maketitle


\section{Introduction}
The goal of this project is to simulate a cache memory system based on the given specifications and trace file. The cache simulation is implemented in C, and the report outlines the approach taken to solve the problem.

\section{Problem Description}
This programme involves reading configuration parameters from a file (\texttt{instruct.txt}) and simulating a cache memory system based on the provided trace file (\texttt{trace.txt}). The configuration parameters include cache size, block size, associativity, replacement policy, and write policy.

\section{Approach}

\subsection{Reading Configuration Parameters}
\begin{enumerate}
    \item Opened the configuration file (\texttt{instruct.txt}) and read the relevant parameters such as cache size, block size, associativity, replacement policy, and write policy.
    \item Parsed the configuration lines to extract integer values and determine cache characteristics.
\end{enumerate}

\subsection{Parsing Trace File}
\begin{enumerate}
    \item Opened the trace file (\texttt{trace.txt}) and read each line to extract information about read or write operations and memory addresses.
    \item Converted hexadecimal memory addresses to binary form and extracted set indices and tags based on the cache configuration.
\end{enumerate}

\subsection{Cache Simulation}
\begin{enumerate}
    \item Implemented a cache array to represent the simulated cache memory.
    \item Utilized the specified replacement policy (FIFO, LRU, or RANDOM) and write policy (Write-Back or Write-Through) to update the cache based on the trace file operations.
    \item Counted the number of cache hits and misses during the simulation.
\end{enumerate}

\subsection{Printing Results}
\begin{enumerate}
    \item Printed the simulation results, including memory addresses, set indices, tags, and whether each access resulted in a hit or miss.
    \item Displayed the total number of cache hits and misses.
\end{enumerate}

\section{Results}
I have implimented all the parts of problem statement mentioned....R W for FIFO,LRU and RANDOM;
\section{Checking with Testcases}
I have checked the code against test cases that are given in the problem statement and some others that i have attached below.
\section{Conclusion}
This report summarizes the approach taken to simulate a cache memory system based on the given configuration and trace files. The implemented C program successfully simulates cache behavior and provides insights into cache hits and misses. The project demonstrates effective file handling, data parsing, and cache simulation techniques.

\end{document}
